---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nobrainr

<!-- badges: start -->
<!-- badges: end -->

The goal of nobrainr is to provide a simple interface to plot plates from the [Mouse Allen Brain Atlas](https://mouse.brain-map.org/experiment/thumbnails/100048576?image_type=atlas).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("matiasandina/nobrainr")
```
## Examples

### Plot atlas plate based on AP

```{r plot-atlas}
library(nobrainr)
## basic example code
plot_atlas(AP = 0,half = F)
```

You can also use the `bw` argument to get the `bw` version.

```{r plot-atlas-bw}
plot_atlas(AP = 0,half = F, bw = T)
```

### Plot multiple atlas plates

A little bit of knowledge in R can help manipulate the resulting `ggplot2` object. We can use `verbose = FALSE` to avoid all the user feedback.

```{r plot-list, warning=F, message=FALSE}
# AP values need not be exact, they are rounded to correct plates
desired_AP <- seq(1, -6, -1)
plot_list <- 
purrr::map(
  desired_AP,
  ~plot_atlas(AP=.x, half=T, verbose=F) + 
    ggplot2::labs(title = glue::glue("AP = {.x} mm"))
)
cowplot::plot_grid(plotlist = plot_list)
```

### Export

If you want to export the plots to an `svg` format for presentation you can use the `ggsave` function from the `ggplot2` package.

```{r ggsave, eval=F}
p1 <- plot_atlas(0)
ggplot2::ggsave(filename = "plot_title.svg", 
                plot = p1) # <- will save to the local directory, check ?ggsave
```


### Plot counts calculated elsewhere

This package comes with data that contains cell counts in different brain regions.

```{r show-trial-df}
trial_df
```

You can plot the counts using `plot_roi_counts()`. 

```{r plot-roi-counts}
plot_roi_counts(trial_df, AP=1.1, half=FALSE)
```

Mind that not all AP levels are present on this sample data. Within each AP, not all ROIs have data either. Because we can't plot nonexistent data, `nobrainr` will throw an error.

```{r error-example, error=TRUE}
plot_roi_counts(count_df = trial_df, AP=1, half=FALSE)
```


## Contribute

This is a preliminary release. Please file [issues](https://github.com/matiasandina/nobrainr/issues) to improve the package.

## Acknowledgements

This package contains data coming from [wholebrain](https://github.com/tractatus/wholebrain) package.
